|

### 2019-09-17 paper.Rmd
caption to illustration

>>>>

\begin{figure*}[ht]
\includegraphics[width=0.4\textwidth]{diagrams/centered-slice.pdf}}
\hspace{5mm}
\centerline{\includegraphics[width=0.4\textwidth]{diagrams/orthogonal-distance.pdf}
\caption{Illustrations of  slicing, through a 3D sphere (left), and deomnstrating the calculation of the orthogonal distance  (right). 3D slicing, can be done by sliding the projection plane along the orthogonal direction: centered at the origin (green) and one off-center at $\mathbf{c}$ (blue). This intuition does not transfer to higher dimensions, and it is best to use orthogonal distance between point and projection plane for computing the slice. Because a projection plane has no specific location, for slicing we can prescribe this, as through the data center, or any other point, $\mathbf{c}$.}
\label{fig:diagrams}
\end{figure*}
